### 2021-12-09 papers/main.tex
TEMPORARY DEPLOY COMMIT

The \(Q\)-function, \(Q^\pi(s,a)\), is defined as the expected reward of taking action
\(a\) in state \(s\) and then following policy \(\pi\) thereafter:
\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=0, a_0=0 \right]\).
The Bellman operator on \(Q^\pi\) is defined as
\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s+t)}
\left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
\(Q\)-function we can define a policy \(\pi(a \vert s) = \arg\max_a Q(s,a)\).
In deep RL, we model \(Q\) with a neural network \(\hat{Q}_\omega\).
One way to facilitate exploration in this policy is to introduce uncertainty in the
\(Q\)-value. \cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over
Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then we approximate this with a
distribution parameterized by \(\phi\) such that
\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
\begin{equation}
    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
\end{equation}
Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
countably generated from \(\state\) they find that \(\omega^\star\) such that
\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
by minimising the mean squared Bayesian Bellman error (MSBBE):
\begin{equation}
    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
\end{equation}
And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
as long as we can sample from \(P(\phi \vert \D_\omega^N)\).

>>>>

The \(Q\)-function, \(Q^\pi(s,a)\), is defined as the expected reward of taking action
\(a\) in state \(s\) and then following policy \(\pi\) thereafter:
\(Q^\pi \defeq \E_\pi \left[ \sum_{t=0}^\infty \gamma^t r_t \vert s_0=0, a_0=0 \right]\).
The Bellman operator on \(Q^\pi\) is defined as
\(\B[Q^\pi](s_t,a_t) \defeq \E_{P(s_{t+1} \vert s_t, a_t)\pi(a_{t+1} \vert s+t)}
\left[ r(s_{t+1}, s_t, a) + \gamma Q^\pi(s_{t+1}, a_{t+1}) \right]\). With the
\(Q\)-function we can define a policy \(\pi(a \vert s) = \arg\max_a Q(s,a)\).
In deep RL, we model \(Q\) with a neural network \(\hat{Q}_\omega\).
One way to facilitate exploration in this policy is to introduce uncertainty in the
\(Q\)-value.
\citet{fortunato_noisy_2019} introduced noisy networks for exploration.
These are networks with stochastic weights, where each weight \(w^{(l)}_{ij}\)
has an added pertrubaition sampled from a noise distribution with standard deviation \(\sigma^{(l)}_{ij}\).
After initializing \(\bm{\mu}\) and \(\bm{\sigma}\) such that the network has sufficient
stochasticity for exploration, both parameters are learned using standard backpropagation.
The approach is similar to variational inference schemes such as bayes by backprop~\cite{blundell_weight_2015} where the weights are normally distributed with mean 
\(\mu^{(l)}_{ij}\) and standard deviation \(\sigma^{(l)}_{ij}\),

\cite{fellows_bayesian_2021} does this by defining the Bayesian Bellman
operator (BBO). They define \(P_B(b \vert s, a, \omega)\) as the distribution over
Bellman functions such that for a noisy sample \(b_i \sim P_B(b \vert s,a,\omega)\),
\(b_i = \B[\hat{Q}_\omega](s_i, a_i) + \eta_i\). Then we approximate this with a
distribution parameterized by \(\phi\) such that
\(P(b \vert s,a,\phi) \approx P(b \vert s,a,\omega)\).
\begin{equation}
    \B_{\omega, N}^\star(s,a) \defeq \E_{P(\phi \vert \D_\omega^N)} \left[ \hat{B}_\phi(s,a) \right].
\end{equation}
Here, \(\hat{B}_\phi(s,a) = \E_{P(b \mid s, a, \phi)}[b]\), is the conditional mean of
\(P(b \vert s, a, \phi)\), and the data \(\D_\omega^N\) is defined as the collection of
sampled \(Q\)-values, states and actions \(\D_\omega^N \defeq \{b_i, s_i, a_i\}_{i=1:N}\).
Under the assumption that each state \(s_i\) is drawn i.i.d from a distribution with
support over \(\state\), or from an ergodic Markov chain defined over a \(\sigma\)-algebra that is
countably generated from \(\state\) they find that \(\omega^\star\) such that
\(\hat{Q}_{\omega^\star} = \B^\star_{\omega^\star, N}\) can be found 
by minimising the mean squared Bayesian Bellman error (MSBBE):
\begin{equation}
    \mathrm{MSBBE}_N(\omega) \defeq \lVert \hat{Q}_{\omega} - \B^\star_{\omega, N} \lVert^2_{\rho, \pi},
\end{equation}
And that an unbiased estimate of \(\nabla_\omega \mathrm{MSBBE}_N(\omega)\) can be calculated
as long as we can sample from \(P(\phi \vert \D_\omega^N)\).
